One more attempt on ArXe

### 2016-05-23 abstract.tex

\begin{abstract}
We report about autoionization channels of Ar inner valence ionized states in mixed ArXe clusters produced by coexpansion of the two gases.
Clusters with a range of sizes were probed, and the Xe content was varied between 10 and 53\,\%. 
Our experimental data obtained by electron, electron coincidence spectroscopy are compared to {\it ab initio} calculations for representative cluster structures.
The combined experimental and theoretical data show that the autoionization of Ar 3s$^{-1}$ in ArXe is dominated by Interatomic Coulombic Decay (ICD) to Xe atoms in the second coordination shell of the originally excited atom.
Electron Transfer Mediated Decay (ETMD) is energetically allowed as well for most cluster structures, but has less intensity in the experimental spectra.
We show experimentally that the relaxation of Ar inner valence states by ICD and ETMD together has an efficiency of unity, within the experimental accuracy, for all clusters expect those with the lowest Xe content.
Decay rates calculated for ETMD favour cluster structures with either a clear seggregation between Ar and Xe fractions, e.g. Xe core, Ar shell systems, or with few Xe atoms singled out in surface sites.
They differ significantly from calculated minimum energy structures for ArXe systems, which might show that the latter structures are not realized in supersonic expansion.
\end{abstract}

>>>>

\begin{abstract}
We report about autoionization channels of Ar inner valence ionized states in mixed ArXe clusters. 
The mixed clusters were produced by supersonic coexpansion of the two gases.
Clusters with a range of sizes and compositions were probed. 
The Xe content in the clusters was varied between 10 and 53\,\%. 
Our experimental data obtained by electron, electron coincidence spectroscopy are compared to {\it ab initio} calculations for representative cluster structures.
The combined experimental and theoretical data show that the autoionization of Ar 3s$^{-1}$ in ArXe is dominated by Interatomic Coulombic Decay (ICD) to Xe atoms in the second coordination shell of the originally excited atom.
Electron Transfer Mediated Decay (ETMD) is energetically allowed as well for most cluster structures, but has less intensity in the experimental spectra.
We show experimentally that the relaxation of Ar inner valence states by ICD and ETMD together has an efficiency of unity, within the experimental accuracy, for all clusters expect those with the lowest Xe content.
Decay rates calculated for ETMD favour cluster structures with either a clear seggregation between Ar and Xe fractions, e.g. Xe core, Ar shell systems, or with few Xe atoms singled out in surface sites.
They differ significantly from calculated minimum energy structures for ArXe systems, which might show that the latter structures are not realized in supersonic expansion.
\end{abstract}

### 2016-05-23 exp_results.tex

\section{Experimental Results
\label{sec:exp_results}}
%
%
\begin{table}
\caption{Properties of the outer valence spectra of mixed ArXe clusters. 
Spectra of pure Ar and Xe clusters are included for reference. 
All spectra were recorded at $h\nu = 17$~eV, except for the pure Xe clusters ($h\nu = 60$~eV). 
Binding energies $\EB$ were determined as the centre of gravity of the respective feature, while band width $w$ are the FWHM of a Gaussian fit. 
The average Xe content of the cluster ensemble, Xe$_{\rm cl}$, was determined from the areas of the respective photolines, corrected by their atomic photoionization cross sections (Ar 33.0 Mb, Xe 51.3 Mb)\cite{samson2002}.
Uncertainties are estimated as $\pm$3\,\% for the Xe content and 0.05~eV for the binding energies. 
For reference, the row labelled `(th.)' gives the binding energies used in the simulations of this paper, and the last row their atomic counterparts. 
Values for Ar 3p in the last row refer to the fine structure states.
\label{tab:valence} }
\begin{tabular}{ l c c c c c c c c}
%
\toprule
 \multicolumn{2}{r}{size} &  Xe$_{\rm in}$& $\EB$ (eV)& $w$ (eV)& \multicolumn{2}{c}{$\EB$ (eV)}  & $w$ (eV) &  Xe$_{\rm cl}$ \\
%
 \multicolumn{2}{r}{(label)}&  (\%) & Ar 3p & Ar 3p & Xe 5p$_{1/2}$ &  Xe 5p$_{3/2}$ & Xe 5p$_{3/2}$  &  (\%) \\
\midrule
% Ar, from Marko
 Ar & (1) &&  15.3  &  1.1 & & & &  \\
% Ar, from Marko 
 Ar & (2) &&  15.1  &  1.3 & & & &  \\
%
%  columns in the following: energies c.g. 51-plt-oval, widths Marko Diss., Xe content Marko Diss
% 1103 676, 679
 ArXe & S &1.2 & 15.36 & 0.9 & 13.07 & 11.75 & 0.85 & 12\\
% 1103 670
 ArXe & M &1.2 & 15.30 & 1.0 & 12.97 & 11.61 & 0.85 & 11\\
% 1103 671
 ArXe & L &1.2 & 15.25 & 1.1 & 12.91 & 11.52 & 1.08 & 10\\
% 1103 663
 ArXe & S &3.0 & 15.39 & 0.8 & 13.06 & 11.68 & 1.02 & 29\\
% 1103 640
 ArXe & M &5.0 & 15.31 & 0.6 & 12.96 & 11.44 & 1.24 & 53\\
% 0506 
 Xe &  & & & & 12.76 & 11.19 & 1.18 & 100\\
%
\midrule
%
%  1004  886  (UHe, c.g. + roi values)
 ArXe & XL &2.5 & 15.15 & 1.3 & 12.59 & 11.01 & 1.24 & 19\\
%
\midrule
% Date: Wed, 20 Jan 2016 11:27:39, From: Elke Fa?hauer <elke.fasshauer@uit.no>
 Ar, Xe & (th.) && 15.3 && 13.0 & 11.5 &&\\
%
 \multicolumn{2}{l}{(atomic)\cite{velchev,sansonetti}} && 15.76|15.94 && 13.43 & 12.13 &&\\
%
\bottomrule
\end{tabular}
\end{table}

@@

Finally, comparing Figure \ref{figure:oval2} to Figure \ref{figure:oval1} reveals
that much larger changes in the valence emission spectra occur for changes in
the expansion conditions than for changes of the gas mixture.
This finding is supported by the spectra shown in Ref.\ \cite{lindblad}.
%
%
\subsection{Inner valence spectra}
%
We now focus on the Ar inner valence (3s) vacancy states. 
%
\begin{figure}[ht]
 \centering
 \includegraphics[width=8.8cm]{pics/figure_ival.pdf}
 \caption{
Photon excited electron spectra of mixed Ar-Xe clusters in the inner valence region.
Symbols show the Ar 3s photoline from clusters (`cl') and uncondensed Ar monomers (`m'), atop of a background resulting from inelastic intracluster scattering of outer valence photoelectrons (`excitonic satellites'\protect\cite{hergenhahn2002}).
Colored symbols result from accumulating photoelectrons only from those events, which resulted in the subsequent emission of a second electron.
Solid lines represent various least-squares fits to the data, see text for details.
A photon energy of $h\nu = 32$ eV was used.
 \label{figure:ival}
 }
\end{figure}

@@

If we produce a spectrum only from those electrons recorded as part of a two-electron coincidence (colored symbols in Figure \ref{figure:ival}), the apparent intensity drops.
This can partly be attributed to the finite detection efficiency of the spectrometer. 
Moreover, the monomer part of the Ar 3s signal completely disappears, as 3s photoionization of an uncondensed Ar atom in the gas jet cannot lead to emission of a second electron. 
Further features of these diagrams and the least squares fits shown in the Figure are discussed below.
%
%
\subsection{ICD/ETMD spectra}
%
\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/figure_icd_12.pdf}
 \caption{
Energy spectrum of all coincident secondary (ICD or ETMD) electrons $e_2$ pertaining to primary electrons $e_1$ in the Ar 3s binding energy region. 
Spectra were recorded with a photon energy of $h\nu = 32$~eV. 
Black symbols with error bars show the data points for the smallest clusters measured (`S'), two larger clusters sizes are shown by the red and blue traces. 
Error bars for the latter are smaller than the ones shown and have been omitted.
For comparison, all spectra are shown area-normalized. 
}
 \label{figure:icd_12}
\end{figure}
%
%
\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/figure_icd_l.pdf}
 \caption{
Energy spectrum of all coincident secondary (ICD or ETMD) electrons $e_2$ for clusters of the same size, but from gas mixtures with different Xe concentration. See Figure \protect\ref{figure:icd_12} for details.
}
 \label{figure:icd_l}
\end{figure}
%
In Figure \ref{figure:icd_12}, we show the spectra of ICD/ETMD electrons pertaining to emission of an Ar 3s cluster photoelectron. 
These, and the following figure, constitute the central experimental result of the article.
Due to their low kinetic energy, without use of a coincidence method they could hardly be separated from the background of inelastically scattered photoelectrons.\cite{mucke}
Further details on the data acquisition and analysis methodology are given in the Supporting Information.
We note here that spectra recorded at $h\nu = 34$ eV as a cross-check, quantitatively agree to those shown in the Figure.

Clearly, spectra for the three different cluster sizes in Figure \ref{figure:icd_12} are significantly different: Spectra for the larger cluster acquire more intensity in the 1-1.5 eV region and have less intensity for energies below 0.5 eV.
In contrast to that, the ICD/ETMD spectrum hardly varies when the composition of the expanding gas mixture is changed (Figure \ref{figure:icd_l}).
The full set of ICD/ETMD spectra is shown as Supporting Information.

>>>>

\section{Experimental Results
\label{sec:exp_results}}
%
%
\begin{table}
\caption{Properties of the outer valence spectra of mixed ArXe clusters. 
Spectra of pure Ar and Xe clusters are included for reference. 
All spectra were recorded at $h\nu = 17$~eV, except for the pure Xe clusters ($h\nu = 60$~eV). 
Binding energies $\EB$ were determined as the centre of gravity of the respective feature, while band width $w$ are the FWHM of a Gaussian fit. 
The average Xe content of the cluster ensemble, Xe$_{\rm cl}$, was determined from the areas of the respective photolines, corrected by their atomic photoionization cross sections (Ar 33.0 Mb, Xe 51.3 Mb)\cite{samson2002}.
Uncertainties are estimated as $\pm$3\,\% for the Xe content and 0.05~eV for the binding energies. 
For reference, the row labelled `(th.)' gives the binding energies used in the simulations of this paper, and the last row their atomic counterparts. 
Values for Ar 3p in the last row refer to the fine structure states.
\label{tab:valence}}
\begin{tabular}{ l c c c c c c c c}
%
\toprule
 \multicolumn{2}{r}{size} &  Xe$_{\rm in}$& $\EB$ (eV)& $w$ (eV)& \multicolumn{2}{c}{$\EB$ (eV)}  & $w$ (eV) &  Xe$_{\rm cl}$ \\
%
 \multicolumn{2}{r}{(label)}&  (\%) & Ar 3p & Ar 3p & Xe 5p$_{1/2}$ &  Xe 5p$_{3/2}$ & Xe 5p$_{3/2}$  &  (\%) \\
\midrule
% Ar, from Marko
 Ar & (1) &&  15.3  &  1.1 & & & &  \\
% Ar, from Marko 
 Ar & (2) &&  15.1  &  1.3 & & & &  \\
%
%  columns in the following: energies c.g. 51-plt-oval, widths Marko Diss., Xe content Marko Diss
% 1103 676, 679
 ArXe & S &1.2 & 15.36 & 0.9 & 13.07 & 11.75 & 0.85 & 12\\
% 1103 670
 ArXe & M &1.2 & 15.30 & 1.0 & 12.97 & 11.61 & 0.85 & 11\\
% 1103 671
 ArXe & L &1.2 & 15.25 & 1.1 & 12.91 & 11.52 & 1.08 & 10\\
% 1103 663
 ArXe & S &3.0 & 15.39 & 0.8 & 13.06 & 11.68 & 1.02 & 29\\
% 1103 640
 ArXe & M &5.0 & 15.31 & 0.6 & 12.96 & 11.44 & 1.24 & 53\\
% 0506 
 Xe &  & & & & 12.76 & 11.19 & 1.18 & 100\\
%
\midrule
%
%  1004  886  (UHe, c.g. + roi values)
 ArXe & XL &2.5 & 15.15 & 1.3 & 12.59 & 11.01 & 1.24 & 19\\
%
\midrule
% Date: Wed, 20 Jan 2016 11:27:39, From: Elke Fa?hauer <elke.fasshauer@uit.no>
 Ar, Xe & (th.) && 15.3 && 13.0 & 11.5 &&\\
%
 \multicolumn{2}{l}{(atomic)\cite{velchev,sansonetti}} && 15.76|15.94 && 13.43 & 12.13 &&\\
%
\bottomrule
\end{tabular}
\end{table}

@@

Finally, comparing Figure \ref{figure:oval2} to Figure \ref{figure:oval1} reveals
that much larger changes in the valence emission spectra occur for changes in
the expansion conditions than for changes of the gas mixture.
This finding is supported by the spectra shown in Ref.\ \citenum{lindblad}.
%
%
\subsection{Inner valence spectra}
%
We now focus on the Ar inner valence (3s) vacancy states. 
%
\begin{figure}[ht]
 \centering
 \includegraphics[width=8.8cm]{pics/figure_ival.pdf}
 \caption{
Photon excited electron spectra of mixed Ar-Xe clusters in the inner valence region.
Symbols show the Ar 3s photoline from clusters (`cl') and uncondensed Ar monomers (`m'), atop of a background resulting from inelastic intracluster scattering of outer valence photoelectrons (`excitonic satellites'\protect\cite{hergenhahn2002}).
Colored symbols result from accumulating photoelectrons only from those events, which resulted in the subsequent emission of a second electron.
Solid lines represent various least-squares fits to the data, see text for details.
A photon energy of $h\nu = 32$ eV was used.
 \label{figure:ival}
 }
\end{figure}

@@

If we produce a spectrum only from those electrons recorded as part of a two-electron coincidence (electron pair with kinetic energies ($e_1,e_2$)) the apparent intensity drops (colored symbols in Figure \ref{figure:ival}).
This can partly be attributed to the finite detection efficiency of the spectrometer. 
Moreover, the monomer part of the Ar 3s signal completely disappears, as 3s photoionization of an uncondensed Ar atom in the gas jet cannot lead to emission of a second electron. 
Further features of these diagrams and the least squares fits shown in the Figure are discussed below.
%
%
\subsection{ICD/ETMD spectra}
%
\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/figure_icd_12.pdf}
 \caption{
Energy spectrum of all coincident secondary (ICD or ETMD) electrons $e_2$ pertaining to primary electrons $e_1$ in the Ar 3s binding energy region. 
Spectra were recorded with a photon energy of $h\nu = 32$~eV. 
Black symbols with error bars show the data points for the smallest clusters measured (`S'), two larger clusters sizes are shown by the red and blue traces. 
Error bars for the latter are smaller than the ones shown and have been omitted.
For comparison, all spectra are shown area-normalized. 
}
 \label{figure:icd_12}
\end{figure}
%
%
\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/figure_icd_l.pdf}
 \caption{
Energy spectrum of all coincident secondary (ICD or ETMD) electrons $e_2$ for clusters of the same size, but from gas mixtures with different Xe concentration. See Figure \protect\ref{figure:icd_12} for details.
}
 \label{figure:icd_l}
\end{figure}
%
In Figure \ref{figure:icd_12}, we show the spectra of ICD/ETMD electrons pertaining to emission of an Ar 3s cluster photoelectron. 
Due to their low kinetic energy, without use of a coincidence method they could hardly be separated from the background of inelastically scattered photoelectrons.\cite{mucke}
These, and the following figure, constitute the central experimental result of the article.
Spectra recorded at $h\nu = 34$ eV as a cross-check quantitatively agree to those shown in the Figure.
This underpins our assignment of this intensity to an autoionization process.
Further details on the data acquisition and analysis methodology, as well as the 34~eV spectra, are given in the Supporting Information.

Spectra for the three different cluster sizes in Figure \ref{figure:icd_12} are significantly different: Spectra for the larger cluster acquire more intensity in the 1-1.5 eV region and have less intensity for energies below 0.5 eV.
In contrast to that, the ICD/ETMD spectrum hardly varies when the composition of the expanding gas mixture is changed (Figure \ref{figure:icd_l}).
The full set of ICD/ETMD spectra is shown as Supporting Information.

### 2016-05-23 experimental.tex

\section{Experimental}
%
\begin{table*}
\caption{
Expansion parameters used for cluster production. 
Here, Xe$_{\rm in}$ is the molar fraction of Xe in the gas mixture before the expansion, $T$ is the nozzle temperature, and $p$ the stagnation pressure. 
Experiments were done with $d = 80~\mu$m (first two sections) and $d = 100~\mu$m (bottom section) conical nozzles of 15$^\circ$ half opening angle. 
Due to the much lower freezing point of Ar, we basically have an Ar seeded expansion of Xe gas. 
$\langle N_{\rm Ar} \rangle$ and $\langle N_{\rm Xe} \rangle$ refer to cluster sizes for a pure Ar, or pure Xe expansion, resp., at the given conditions, calculated from a scaling law.\protect\cite{hagena1981}
We expect actual cluster sizes in-between these two limiting values. 
Inaccuracies in the calculation of $\langle N\rangle$ due to fluctuations of the input parameters are less than 6\,\%. This figure does not include systematic errors of the empirical model.
}
\label{tab:cluster}

@@

Prediction of the sizes of clusters from a supersonic expansion mainly rests on empirical scaling laws,\cite{hagena1981} which have been the subject of some discussion.
Recent analyses of photoionization spectra suggests that mean sizes arrived at by scaling laws are smaller than the actual size, at least for rare gas clusters in the range $\langle N\rangle < 1000$.\cite{bergersen,hergenhahnprb,foerstel_arg2_2011}
Moreover, such scaling laws originally were derived only for pure gas expansions.
A recent investigation of cluster sizes in a mixed Ar-Kr expansion yielded a revised scaling law, which essentially amounts to the use of a weighted average over the atom-specific parameters of the two gases.\cite{danylchenko2015} 
Although the analogy to our case is not complete, as phase segregation occurs in Ar-Kr to a much lesser extent,\cite{Vach_1999,lundwall_arkr} we therefore expect actual cluster sizes between the values calculated for Ar and Xe.

The expansion chamber for the supersonic jet is separated from the interaction chamber by a non-magnetic, conical skimmer with a diameter 1~mm opening (Beam Dynamics). 
At few cm distance behind the skimmer, the cluster jet was crossed by synchrotron radiation from the BESSY electron storage ring at Helmholtz-Zentrum Berlin. 
Electrons were detected by a short `magnetic bottle' time-of-flight spectrometer, that has been described earlier.\cite{mucke_review}
Due to its large collection angle, this instrument is particularly suited for experiments that employ electron-electron coincidence detection.
Data were recorded in two different beamtimes at the UE112-PGM-1 (small and medium sized clusters, first two sections in Table \ref{tab:cluster}) and at the TGM-4 beamline (large clusters, last section in Table \ref{tab:cluster}). 
Linearly, horizontally polarized radiation was used. 
The storage ring was operated in single bunch conditions.
Spectra of pure Ar clusters shown for comparison are from Ref. \citenum{foerstel_arg2_2011}, and a spectrum of pure Xe clusters was recorded with the set-up described in Ref. \citenum{hergenhahnprb}.

Entrance aperture and drift tube of the magnetical bottle spectrometer can be independently biased to influence the electron flight times. 
For the data shown here, slightly positive bias voltages were used (+1.8 V to +2.2 V) in order to have all electrons arriving at the detector within one BESSY single bunch period (800 ns). 
The detection efficiency was determined as 0.6, with the method outlined in Ref. \citenum{mucke_review}.

>>>>

\section{Experimental}
%
\begin{table*}
\caption{
Expansion parameters used for cluster production. 
Here, Xe$_{\rm in}$ is the molar fraction of Xe in the gas mixture before the expansion, $T$ is the nozzle temperature, and $p$ the stagnation pressure. 
Experiments were done with $d = 80~\mu$m (first two sections) and $d = 100~\mu$m (bottom section) conical nozzles of 15$^\circ$ half opening angle. 
We basically have an Ar seeded expansion of Xe gas, as the freezing point of Ar is much lower. 
$\langle N_{\rm Ar} \rangle$ and $\langle N_{\rm Xe} \rangle$ refer to cluster sizes for a pure Ar, or pure Xe expansion, resp., at the given conditions, calculated from a scaling law.\protect\cite{hagena1981}
We expect actual cluster sizes in-between these two limiting values. 
Inaccuracies in the calculation of $\langle N\rangle$ due to fluctuations of the input parameters are less than 6\,\%. This figure does not include systematic errors of the empirical model.
}
\label{tab:cluster}

@@

Prediction of the sizes of clusters from a supersonic expansion mainly rests on empirical scaling laws,\cite{hagena1981} which have been the subject of some discussion.
Moreover, such scaling laws originally were derived only for pure gas expansions.
A recent investigation of cluster sizes in a mixed Ar-Kr expansion yielded a revised scaling law, which essentially amounts to the use of a weighted average over the atom-specific parameters of the two gases.\cite{danylchenko2015} 
Although the analogy to our case is not complete, as phase segregation occurs in Ar-Kr to a much lesser extent,\cite{Vach_1999,lundwall_arkr} we therefore expect scaling law cluster sizes between the values calculated for Ar and Xe.
Recent analyses of photoionization spectra suggests that mean sizes arrived at by scaling laws are smaller than the actual size, at least for rare gas clusters in the range $\langle N\rangle < 1000$.\cite{bergersen,hergenhahnprb,foerstel_arg2_2011}
We expansion conditions labelled `S'-`L', we therefore expect that the scaling law estimates are a lower boundary for the actual cluster size.

The expansion chamber for the supersonic jet is separated from the interaction chamber by a non-magnetic, conical skimmer with a diameter 1~mm opening (Beam Dynamics). 
At few cm distance behind the skimmer, the cluster jet was crossed by synchrotron radiation from the BESSY electron storage ring at Helmholtz-Zentrum Berlin. 
Electrons were detected by a short `magnetic bottle' time-of-flight spectrometer, that has been described earlier.\cite{mucke_review}
Due to its large collection angle, this instrument is particularly suited for experiments that employ electron-electron coincidence detection.
Data were recorded in two different beamtimes at the UE112-PGM-1 (small and medium sized clusters, first two sections in Table \ref{tab:cluster}) and at the TGM-4 beamline (large clusters, last section in Table \ref{tab:cluster}). 
Linearly, horizontally polarized radiation was used. 
The storage ring was operated in single bunch conditions.
Spectra of pure Ar clusters shown for comparison are from Ref.\ \citenum{foerstel_arg2_2011}, and a spectrum of pure Xe clusters was recorded with the set-up described in Ref.\ \citenum{hergenhahnprb}.

Entrance aperture and drift tube of the magnetical bottle spectrometer can be independently biased to influence the electron flight times. 
For the data shown here, slightly positive bias voltages were used (+1.8 V to +2.2 V) in order to have all electrons arriving at the detector within one BESSY single bunch period (800 ns). 
The detection efficiency was determined as 0.6, with the method outlined in Ref.\ \citenum{mucke_review}.

The high detection efficiency of the instrument is a pre-requisite for measuring two-electron emission processes, such as photoelectron emission followed by ICD or ETMD, by using electron-electron coincidence detection. 
This allows to filter the full electron spectrum for contributions arising after emission of an Ar 3s photoelectron.
ICD/ETMD spectra presented here are based on this method, which has been explained earlier.\cite{mucke_review,Foerstel_phd}
Technical details and full electron-electron coincidence spectra are given in the Supporting Information.

### 2016-05-23 intro.tex

The plan of our paper is as follows: ...

>>>>

The plan of our paper is as follows: We firstly delineate our experimental and theoretical methods. 
Calculations were done for a number of model structures which were systematically varied, and are described in the following section.
After that, we describe and discuss our theoretical results for the autoionization spectra of the model clusters.
Experimental results are then shown and possible conclusions from comparing them to the calculations are given.
Details on the experimental technique, and calculated spectra for a wider range of structures are given as Supporting Information.

### 2016-05-23 theo_discussion.tex

\section{Discussion
\label{sec:discussion}}
%
%We have discussed the experimental spectra in Section \ref{sec:exp_results} and
%the expected features of spectra for different cluster types in
%Section \ref{sec:th_results}. In this section we combine the experimental and theoretical
%results in order to determine the structure of the noble gas clusters.
%
%The simulated secondary electron spectra for the xenon core structures
%(see Figure \ref{figure:xe_3_in})
%show an ICD peak at higher energies than those structures with added xenon
%atoms on the surface. This does not fit to the experimentally determined
%spectra and hence we consider an argon core to be more probable for the
%small measured clusters.
%
%The experimental spectra in Figure \ref{}
%show a broadening of the secondary electron peak with increasing
%pressure (?) and hence cluster size just as can be expected from
%the theoretically simulated spectra in Figure \ref{figure:surf}.
%
%From the theoretical simulations of larger small clusters
%having the same xenon content as experimentally observed a clearly
%visible ETMD peak is to be expected as shown in Figure \ref{figure:ar_3_6in}.
%However, the experimental spectra do not show a signal in the energy
%region of \unit[1.5--6.5]{eV}. From this we conclude that the clusters
%measured were smaller than 55 atoms containing only very few xenon atoms.
%Additionally, if the cluster contains more than one xenon atom, they are
%not expected to be close because of an otherwise visible ETMD peak
%(compare Figure \ref{figure:2tops}).
%
%The large clusters with a large xenon content can be expected to have
%a xenon core being surrounded by argon layers and hence, both ICD and
%ETMD should be visible in the spectrum. Unfortunately, the ICD and ETMD
%peaks overlap such that the two processes can not be distiguished.
%
We now would like to interpret our experimental findings in view of the simulated results described in Section `Theoretical Results'.
Figure \ref{figure:eff} shows that for Ar 3s$^{-1}$ states autoionization by either ICD or ETMD is the only mode of relaxation, except for the clusters with the smallest Xe content.
We consider this a remarkable result, because the ICD decay path in this system is only possible with a Xe atom in the second coordination shell (or further shells).
ETMD may take place between Ar and two Xe neighbours, but this channel has often been found less probable than ICD.\cite{zobeley}
Nevertheless, even in this situation radiative decay channels appear to be less probable.

% lowest kinetic energy is the first point of energy raster for t-E code of 52-proc-spec
Structurally, all experimental ICD/ETMD spectra have a maximum at or near the lowest kinetic energy that could be measured (50~meV), and decrease in intensity to less than half for kinetic energies below one eV. 
Qualitatively, this shape fits to the ICD contributions to the autoionization spectra discussed in the `Theory' section, but not the ones from ETMD. These calculated spectra have a typical three-fold structure with peaks between 3.5-5~eV, 1.5-2.5~eV and around 0 eV kinetic energy. 
The former two features seem not to be present in the experimental spectra. 
Due to restrictions in the detector electronics, electron pairs with very similar kinetic energy cannot be detected. 
The highest kinetic energy for an autoionization electron that can be detected in coincidence with a photoelectron of $\sim3.5$~eV ($h\nu = 32$~eV) is around 2.5~eV.
Very weak intensity is observed at this energy, and also at higher $e_2$ energy that can be probed at $h\nu = 34$~eV (Supporting Information).

@@

We are therefore lead to the conclusion that the autoionization spectra we incur are dominated by ICD to non-nearest neighbour atoms, while the intensity of the ETMD channel is low. 
We would like to recall the factors that lead to a propensity for decay via ICD, which have been discussed in the `Theoretical Results'-section.
For ETMD to occur with a measurable rate, two Xe atoms have to be present in the vincinity of the decaying Ar atom (Figure \ref{figure:2tops}).
Should that be the case for a large part of the Ar atoms in some structure, ETMD can even dominate over ICD (Figure \ref{figure:ar_3_6in} and Supporting Information).
Model structures shown in Figures \ref{figure:2tops} and \ref{figure:ar_3_6in} have a Xe content similar to the lowest one probed in our experiment ($\sim$11\,\%).
For a higher Xe content, ETMD will always dominate the spectra if the two species are given the chance to mix, as e.g. in the calculated minimum energy structures of $N=38$ ArXe clusters (Supporting Info.).
For core-shell systems however, the percentage of decay via ETMD stays below 25\,\% even a Xe content above 50\,\% (Table \ref{table:theo_gammas}).

In summary, the two structural motifes that can best be reconciled with our experimental data are
\begin{enumerate}
	\item small clusters containing only few Xe atoms that are spread out to distant positions on the cluster surface, and
	\item systems with a compact Xe core and Ar outer layers.
\end{enumerate}
As even in these two cases intensities would not vanish completely, we have to leave it open though whether other mechanisms are present, which further suppress ETMD vs. ICD.

>>>>

\section{Discussion
\label{sec:discussion}}
%
%We have discussed the experimental spectra in Section \ref{sec:exp_results} and
%the expected features of spectra for different cluster types in
%Section \ref{sec:th_results}. In this section we combine the experimental and theoretical
%results in order to determine the structure of the noble gas clusters.
%
%The simulated secondary electron spectra for the xenon core structures
%(see Figure \ref{figure:xe_3_in})
%show an ICD peak at higher energies than those structures with added xenon
%atoms on the surface. This does not fit to the experimentally determined
%spectra and hence we consider an argon core to be more probable for the
%small measured clusters.
%
%The experimental spectra in Figure \ref{}
%show a broadening of the secondary electron peak with increasing
%pressure (?) and hence cluster size just as can be expected from
%the theoretically simulated spectra in Figure \ref{figure:surf}.
%
%From the theoretical simulations of larger small clusters
%having the same xenon content as experimentally observed a clearly
%visible ETMD peak is to be expected as shown in Figure \ref{figure:ar_3_6in}.
%However, the experimental spectra do not show a signal in the energy
%region of \unit[1.5--6.5]{eV}. From this we conclude that the clusters
%measured were smaller than 55 atoms containing only very few xenon atoms.
%Additionally, if the cluster contains more than one xenon atom, they are
%not expected to be close because of an otherwise visible ETMD peak
%(compare Figure \ref{figure:2tops}).
%
%The large clusters with a large xenon content can be expected to have
%a xenon core being surrounded by argon layers and hence, both ICD and
%ETMD should be visible in the spectrum. Unfortunately, the ICD and ETMD
%peaks overlap such that the two processes can not be distiguished.
%
We now would like to interpret our experimental findings in view of the simulated results described in Section `Theoretical Results'.
Figure \ref{figure:eff} shows that for Ar 3s$^{-1}$ states autoionization by either ICD or ETMD is the only mode of relaxation, except for the clusters with the smallest Xe content.
We consider this a remarkable result, because ICD in this system is only possible with a Xe atom in the second coordination shell of the decaying Ar vacancy (or shells even further apart), which reduces its decay rate.
Also decay rates for ETMD were found to be small in early studies of this effect.\cite{zobeley}
Nevertheless, even in this situation the non-local autoionization channels foreclose radiative decay.

% lowest kinetic energy is the first point of energy raster for t-E code of 52-proc-spec
Structurally, all experimental ICD/ETMD spectra have a maximum at or near the lowest kinetic energy that could be measured (50~meV), and decrease in intensity to less than half for kinetic energies below one eV. 
Qualitatively, this shape fits to the ICD contributions in the autoionization spectra discussed in the `Theory' section, but not to the ones from ETMD. 
The calculated ETMD spectra have a typical three-fold structure with peaks between 3.5-5~eV, 1.5-2.5~eV and around 0 eV kinetic energy. 
The former two features seem not to be present in the experimental spectra. 
Due to restrictions in the detector electronics, electron pairs with very similar kinetic energy cannot be detected. 
The highest kinetic energy for an autoionization electron that can be detected in coincidence with a photoelectron of $\sim3.5$~eV ($h\nu = 32$~eV) is around 2.5~eV.
Very weak intensity is observed at this energy, and also at higher $e_2$ energies that can be probed at $h\nu = 34$~eV (Supporting Information).

@@

We are therefore lead to the conclusion that the autoionization spectra we incur are dominated by ICD to non-nearest neighbour atoms, while the intensity of the ETMD channel is low. 
We would like to recall the factors that lead to a propensity for decay via one or the other mechanism, which have been discussed in the `Theoretical Results'-section.
For ETMD to occur with a measurable rate, two Xe atoms have to be present in the vincinity of the decaying Ar atom (Figure \ref{figure:2tops}).
Should that be the case for a large part of the Ar atoms in some structure, ETMD can even dominate over ICD (Figure \ref{figure:ar_3_6in} and Supporting Information).
Model structures shown in Figures \ref{figure:2tops} and \ref{figure:ar_3_6in} have a Xe content similar to the lowest one probed in our experiment ($\sim$11\,\%).
For a higher Xe content, ETMD will always dominate the spectra if the two species are given the chance to mix, as e.g. in the calculated minimum energy structures of $N=38$ ArXe clusters (Supporting Info).
On the other hand, in core-shell systems decay via ETMD is probable only for Ar atoms in the interface layer, as this mechanism requires some wavefunction overlap between Ar and one of the Xe atoms involved.
For the core-shell systems we have investigated, the likelihood of decay via ETMD stays below 25\,\% even for a Xe content above 50\,\% (Table \ref{table:theo_gammas}).

In summary, the two structural motifes that can best be reconciled with our experimental data are
\begin{enumerate}
	\item small clusters containing only few Xe atoms that are spread out to distant positions on the cluster surface, and
	\item systems with a compact Xe core and Ar outer layers.
\end{enumerate}
These structures are compatible with the findings of Lindblad {\it et al.}\ from core level photoelectron spectroscopy, who proposed the former structure for the smallest clusters in their study, and the latter for larger ones.\cite{lindblad}
As even in these two cases intensity for decay via ETMD would not vanish completely, we have to leave it open though whether other mechanisms are present, which further suppress ETMD vs. ICD.

### 2016-05-23 theo_results.tex

>>>>

We also note that the percentage of decay via ICD is practically independent of the Xe content. 
This can be expected, as ETMD takes place via an exchange transition matrix element, which requires some wavefunction overlap.
ETMD therefore mainly takes place in the Ar atoms at the interface layer to the

### 2016-05-23 theory.tex

\begin{figure}[h]
 \centering
 \includegraphics[width=8.5cm]{pics/channel_open_ICD.pdf}
 \caption{Initial (black trace) and final state energies (blue traces) 
          for ICD in ArXe pairs as a function of 
          internuclear distance, using the experimental ionization potentials given
          in Table \ref{}. For distances larger than the channel opening
          distance the ICD channel is open.}
 \label{figure:channel_open_ICD}
\end{figure}

>>>>

\begin{figure}[h]
 \centering
 \includegraphics[width=8.5cm]{pics/channel_open_ICD.pdf}
 \caption{Initial (black trace) and final state energies (blue traces) 
          for ICD in ArXe pairs as a function of 
          internuclear distance, using the experimental ionization potentials given
          in Table \ref{tab:valence}. For distances larger than the channel opening
          distance the ICD channel is open.}
 \label{figure:channel_open_ICD}
\end{figure}
